### 2021-09-06 README.Rmd
add some figures to the readme

``` r
# install.packages("devtools")
devtools::install_github("njtierney/conmat")
```

>>>>

``` r
# install.packages("remotes")
remotes::install_github("njtierney/conmat")
```

## Example

```{r}
library(conmat)
# build synthetic age-structured contact matrices with GAMs
# analysis of polymod data

# set age breaks
age_breaks_5y <- c(seq(0, 75, by = 5), Inf)
age_breaks_1y <- c(seq(0, 100, by = 1), Inf)

# fit a single overall contact model to polymod
m_all <- fit_single_contact_model(
  contact_data = get_polymod_contact_data("all"),
  population = get_polymod_population()
)

m_all
```

```{r}
# predict contacts at 1y and 5y resolutions for inspection
synthetic_all_5y <- predict_contacts(
  model = m_all, 
  population = get_polymod_population(),
  age_breaks = age_breaks_5y
) %>%
  predictions_to_matrix()

synthetic_all_5y
```

```{r}
# predict contacts at 1y and 5y resolutions for inspection
synthetic_all_5y <- predict_contacts(
  model = m_all, 
  population = get_polymod_population(),
  age_breaks = age_breaks_5y
) %>%
  predictions_to_matrix()

synthetic_all_5y

library(ggplot2)
plot_matrix(synthetic_all_5y) +
  ggtitle("synthetic all at once")
```
